BANTER for Beaked Whales: South Atlantic

### 2023-06-08 satlantic/beakerBanter_satlantic.Rmd
Major revisions for draft
Revised all datasets and created draft manuscript

---
title: 'BANTER for Beaked Whales: South Atlantic'
author: "Shannon Rankin"
date: "2023-02-08"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# When this rmarkdown file is knit:
# FALSE means it will used saved .rds files instead of re-processing
# TRUE will run everything from scratch - this will take a long time
freshRun <- FALSE
```

@@

```{r, load packages, message=FALSE}
library (PAMpal)
library(banter)
library(rfPermute)
library(kableExtra)
library(readxl)
library(stringr)
library(here)
here()
```

@@

```{r, read acoustic study, include=FALSE, eval=!freshRun}
data <- readRDS('satlantic_study.rds')
# Double check warning messages
print(getWarnings(data)$message)
```

@@

@@

```{r, assign species ID}
GU1605 <- read_excel("GU1605_PG_OfflineEvents_20210809.xlsx", sheet = "BWonly")#read in data
GU1605 <- filter(GU1605, !eventType == "BRAN")
#create formatted event/species dataframe 
speciesID <- GU1605[c("Id", "Species", "Database")] %>% 
  mutate("event" = paste(Database, Id, sep=".OE")) %>% 
  rename("species" = "Species") %>% 
  mutate("species" = str_replace_all(species, "'", ""),
         "species" = str_replace(species, "Sowerby", "Sowerbys"),
         "species" = str_replace(species, "Blainville", "Blainvilles"),
         "species" = str_replace(species, "Cuvier", "Cuviers")) %>% 
  select(all_of(c("event", "species")))

@@

```{r, filter unwanted data}
goodSpecies<- c(c("Blainvilles", "Trues", "Cuviers", "Sowerbys", "Gervais"))
data <- filter(data, species %in% goodSpecies)
```

@@

### *Model without ICI*

1.  Load data, initialize a BANTER model, and create an initial BANTER
    detector model (stage 1).

```{r, read banter model, include=FALSE, eval=!freshRun}
banter_model <- readRDS('satlantic_banter_model_t1e4s2_t1e5s1.rds')
```

```{r, banter detector model, eval=freshRun}
banter_model <- initBanterModel(banter_data$events)
banter_model <- addBanterDetector(banter_model, banter_data$detectors, ntree=1e4, sampsize=2, importance = TRUE)
```

Check for stability (are more trees needed?) before moving on

```{r, banter detector model stability}
plotDetectorTrace(banter_model, detector = paste0('Click_Detector_', 3:4))
plotDetectorTrace(banter_model, detector = paste0('Click_Detector_', 5:6))
summary(banter_model)
```

2.  Run BANTER Event Model (stage 2)

```{r, banter event model}
banter_model <- runBanterModel(banter_model, ntree=1e5, sampsize=1)
summary(banter_model)
```

Check for stability (are more trees needed?). If acceptable, save model
with tree/sampsize info in the filename.

```{r,save banter model, eval=freshRun}
saveRDS(banter_model, 'satlantic_banter_model_t1e4s2_t1e5s1.rds')
```

@@

1.  Load data, initialize a BANTER model, and create an initial BANTER
    detector model (stage 1).

```{r, read banter ici model, include=FALSE, eval=!freshRun}
banter_model_ici <- readRDS('satlantic_banter_model_ici_t1e4s4_t1e5s1.rds')
```

```{r, banter ici detector model, eval=freshRun}
banter_model_ici <- initBanterModel(banter_data_ici$events)
banter_model_ici <- addBanterDetector(banter_model_ici, banter_data_ici$detectors, ntree=1e4, sampsize=4, importance = TRUE)
```

Check for stability to see if we need more trees

```{r, banter ici detector model stability}
plotDetectorTrace(banter_model, detector = paste0('Click_Detector_', 3:4))
plotDetectorTrace(banter_model, detector = paste0('Click_Detector_', 5:6))
summary(banter_model_ici)
```

2.  Run BANTER Event Model (stage 2)

```{r, banter ici event model}
banter_model_ici <- runBanterModel(banter_model_ici, ntree=1e5, sampsize=1)
summary(banter_model_ici)
```

Check for stability (are more trees needed?). If acceptable, save model
with tree/sampsize info in the filename.

```{r, save banter ici model, eval=freshRun}
saveRDS(banter_model_ici, 'satlantic_banter_model_ici_t1e4s4_t1e5s1.rds')
```

@@

First, identify the model you would like to examine (comment out the
model you [do not]{.underline} want to examine).

```{r, identify model}
model <- banter_model
modelname <- "banter_model"

model_ici <- banter_model_ici
modelname_ici <- "banter_model_ici"
```

@@

```{r, extract RF model, include=TRUE}
banter_model_RF <- getBanterModel(model)
banter_model_ici_RF <- getBanterModel(model_ici)
```

@@

```{r, confusion matrix, include=TRUE}
satlantic_confuseMatrix <- rfPermute::confusionMatrix(banter_model_RF)
satlantic_confuseMatrix <- kable(satlantic_confuseMatrix, align = "c", digits = c(0,0,0,0,2,2,2))%>%
  kable_classic()%>%
  column_spec(4, border_right = TRUE)%>%
  row_spec(0, bold = TRUE)%>%
  row_spec(3,hline_after = TRUE)%>%
  row_spec(4, bold = TRUE)%>%
  save_kable(paste(modelname, "satlantic_confuseMatrix.png", sep="_"), zoom = 2)

satlantic_ici_confuseMatrix <- rfPermute::confusionMatrix(banter_model_ici_RF)
satlantic_ici_confuseMatrix <- kable(satlantic_ici_confuseMatrix, align = "c", digits = c(0,0,0,0,2,2,2))%>%
  kable_classic()%>%
  column_spec(4, border_right = TRUE)%>%
  row_spec(0, bold = TRUE)%>%
  row_spec(3,hline_after = TRUE)%>%
  row_spec(4, bold = TRUE)%>%
  save_kable(paste(modelname_ici, "satlantic_ici_confuseMatrix.png", sep="_"), zoom = 2)

@@

![](banter_model_satlantic_confuseMatrix.png)

@@

```{r, proximity plot, include=TRUE}
png(paste(modelname, "satlantic_proximity.png", sep="_"), width = 20, height = 20, units = 'cm', res = 300)
satlantic_proximityPlot <- plotProximity(banter_model_RF)
dev.off()
satlantic_proximityPlot <- plotProximity(banter_model_RF)

png(paste(modelname_ici, "satlantic_proximity.png", sep="_"), width = 20, height = 20, units = 'cm', res = 300)
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF)
dev.off()
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF)
```

@@

```{r, importance heat map, include=TRUE}
png(paste(modelname, "satlantic_importance.png", sep="_"), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_RF, plot.type="heatmap")
dev.off()
satlantic_importance <- plotImportance(banter_model_RF, plot.type="heatmap")

png(paste(modelname_ici, "satlantic_importance.png", sep="_"), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap")
dev.off()
ici_satlantic_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap")
```

@@

```{r, plot votes, include=TRUE}
png(paste(modelname, "satlantic_votes.png", sep="_"), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_RF)
dev.off()
satlantic_votes <- plotVotes(banter_model_RF)

png(paste(modelname_ici, "satlantic_votes.png", sep="_"), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_ici_RF)
dev.off()
ici_satlantic_votes <- plotVotes(banter_model_ici_RF)
```

```{r, class priors, include=TRUE}
satlantic_priors <- classPriors(banter_model_RF, NULL)
```

Plot Confusion Matrix Heat Map

```{r, confusion matrix heat map, include=TRUE}
plotConfMat(banter_model_RF, title="ConfusionMatrix", plot=TRUE)
```

Plot Error Trace for Banter Model

```{r, model error trace, include=TRUE}
plot(banter_model_RF)
```

@@

```{r, predicted probabilities, include=TRUE}
plotPredictedProbs(banter_model_RF, bins=30, plot=TRUE)
```

>>>>

---
title: 'BANTER for Beaked Whales: South Atlantic'
author: "Shannon Rankin"
date: "2023-05-17"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# When this rmarkdown file is knit:
# FALSE means it will used saved .rds files instead of re-processing
# TRUE will run everything from scratch - this will take a long time
freshRun <- FALSE
```
###Organizational Instructions
Save this file in an R Project that includes the following foldering:
/Project
  |-Database/
  |-Binaries/
  |-Figures/
  |-satlantic
    |_ beakerBanter_satlantic.Rmd
    |_ GU1605_PG_OfflineEvents_20210809.xlsx
    |_ satlantic_banter_data.rds
    |_ satlantic_banter_data_ici.rds
    |_ satlantic_banter_model_ec_t1e4s2_t1e5s1.rds
    |_ satlantic_banter_model_ici_t1e4s4_t1e5s1.rds
    |_ satlantic_banter_model_alt_t1e4s4_t1e5s2.rds

@@

```{r, load packages, message=FALSE}
library("easypackages")
libraries("PAMpal", "banter", "rfPermute", "kableExtra", "readxl", "stringr", "magick", "magrittr", "here")
here()
```

@@

@@

```{r, read acoustic study, include=FALSE, eval=!freshRun}
data <- readRDS(here('satlantic', 'satlantic_study.rds'))
# Double check warning messages
print(getWarnings(data)$message)
```

@@

```{r, assign species ID, eval=freshRun}
GU1605 <- read_excel("GU1605_PG_OfflineEvents_20210809.xlsx", sheet = "BWonly")#read in data
GU1605 <- filter(GU1605, !eventType == "BRAN")
#create formatted event/species dataframe 
speciesID <- GU1605[c("Id", "Species", "Database")] %>% 
  mutate("event" = paste(Database, Id, sep=".OE")) %>% 
  rename("species" = "Species") %>% 
  mutate("species" = str_replace_all(species, "'", ""),
         "species" = str_replace(species, "Sowerby", "Sowerbys"),
         "species" = str_replace(species, "Blainville", "Blainvilles"),
         "species" = str_replace(species, "Cuvier", "Cuviers")) %>% 
  select(all_of(c("event", "species")))

@@

```{r, filter unwanted data, eval=freshRun}
goodSpecies<- c(c("Blainvilles", "Trues", "Cuviers", "Sowerbys", "Gervais"))
data <- filter(data, species %in% goodSpecies)
```

@@

### *EC (only) Model*

Initialize, Run & Evaluate Detector Model (stage 1).
```{r, banter ec detector model, eval=freshRun}
banter_model_ec <- initBanterModel(banter_data$events)
banter_model_ec <- addBanterDetector(banter_model_ec, banter_data$detectors, ntree=1e4, sampsize=2, importance = TRUE)

plotDetectorTrace(banter_model_ec, detector = paste0('Click_Detector_', 3:4))
plotDetectorTrace(banter_model_ec, detector = paste0('Click_Detector_', 5:6))
summary(banter_model_ec)
```

Run BANTER Event Model (stage 2)
```{r, banter ec event model, eval=freshRun}
banter_model_ec <- runBanterModel(banter_model_ec, ntree=1e5, sampsize=1)
summary(banter_model_ec)
```

Once a stable model is identified, save model with tree/sampsize info in the filename.
```{r,save banter ec model, eval=freshRun}
saveRDS(banter_model_ec, 'satlantic_banter_model_ec_t1e4s2_t1e5s1.rds')
```

@@

Initialize, Run & Evaluate Detector Model (stage 1)
```{r, banter ici detector model, eval=freshRun}
banter_model_ici <- initBanterModel(banter_data_ici$events)
banter_model_ici <- addBanterDetector(banter_model_ici, banter_data_ici$detectors, ntree=1e4, sampsize=4, importance = TRUE)

plotDetectorTrace(banter_model_ici, detector = paste0('Click_Detector_', 3:4))
plotDetectorTrace(banter_model_ici, detector = paste0('Click_Detector_', 5:6))
summary(banter_model_ici)
```

Run BANTER Event Model (stage 2)
```{r, banter ici event model, eval=freshRun}
banter_model_ici <- runBanterModel(banter_model_ici, ntree=1e5, sampsize=1)
summary(banter_model_ici)
```

Once a stable model is identified, save model with tree/sampsize info in the filename.
```{r, save banter ici model, eval=freshRun, eval=freshRun}
saveRDS(banter_model_ici, 'satlantic_banter_model_ici_t1e4s4_t1e5s1.rds')
```

### Alternative Model (EC_ICI_ALT) with larger sampsize

Initialize, Run & Evaluate Detector Model (stage 1)
```{r, banter alt detector model, eval=freshRun}
banter_model_alt <- initBanterModel(banter_data_ici$events)
banter_model_alt <- addBanterDetector(banter_model_alt, banter_data_ici$detectors, ntree=1e4, sampsize=4, importance = TRUE)

plotDetectorTrace(banter_model_alt, detector = paste0('Click_Detector_', 3:4))
plotDetectorTrace(banter_model_alt, detector = paste0('Click_Detector_', 5:6))
summary(banter_model_alt)
```

Run BANTER Event Model (stage 2)
```{r, banter alt event model, eval=freshRun}
banter_model_alt <- runBanterModel(banter_model_alt, ntree=1e5, sampsize=2)
summary(banter_model_alt)
```

Once a stable model is identified, save model with tree/sampsize info in the filename.
```{r, save banter alt model, eval=freshRun, eval=freshRun}
saveRDS(banter_model_alt, 'satlantic_banter_model_alt_t1e4s4_t1e5s2.rds')
```

@@

First, load the models (if not a fresh run)
```{r, read banter models, include=FALSE, eval=!freshRun}
banter_model_ec <- readRDS(here('satlantic', 'satlantic_banter_model_ec_t1e4s2_t1e5s1.rds'))
banter_model_ici <- readRDS(here('satlantic', 'satlantic_banter_model_ici_t1e4s4_t1e5s1.rds'))
banter_model_alt <- readRDS(here('satlantic', 'satlantic_banter_model_alt_t1e4s4_t1e5s2.rds'))
```

Identify the model you would like to examine (comment out the
model you [do not]{.underline} want to examine).

```{r, identify model}
model_ec <- banter_model_ec
modelname_ec <- "banter_model_ec"

model_ici <- banter_model_ici
modelname_ici <- "banter_model_ici"

model_alt <- banter_model_alt
modelname_alt <- "banter_model_alt"
```

@@

```{r, extract RF model, include=TRUE}
banter_model_ec_RF <- getBanterModel(model_ec)
banter_model_ici_RF <- getBanterModel(model_ici)
banter_model_alt_RF <- getBanterModel(model_alt)
```

```{r, class priors, include=TRUE}
satlantic_ec_priors <- classPriors(banter_model_ec_RF, NULL)[,1]
satlantic_ici_priors <- classPriors(banter_model_ici_RF, NULL)[,1]
satlantic_alt_priors <- classPriors(banter_model_alt_RF, NULL)[,1]
```

@@

```{r, confusion matrix, include=TRUE}
satlantic_ec_confuseMatrix <- rfPermute::confusionMatrix(banter_model_ec_RF)
satlantic_ec_confuseMatrix <- cbind(satlantic_ec_confuseMatrix, priors = satlantic_ec_priors)
satlantic_ec_confuseMatrix <- kable(satlantic_ec_confuseMatrix, align = "c", digits = c(0,0,0,0,2,2,2))%>%
  kable_classic()%>%
  column_spec(6, border_right = TRUE)%>%
  row_spec(0, bold = TRUE)%>%
  row_spec(3,hline_after = TRUE)%>%
  row_spec(6, bold = TRUE)%>%
  save_kable('../manuscript/manuscript_files/satlantic_ec_confuseMatrix.png', zoom = 9)

satlantic_ici_confuseMatrix <- rfPermute::confusionMatrix(banter_model_ici_RF)
satlantic_ici_confuseMatrix <- cbind(satlantic_ici_confuseMatrix, priors = satlantic_ici_priors)
satlantic_ici_confuseMatrix <- kable(satlantic_ici_confuseMatrix, align = "c", digits = c(0,0,0,0,2,2,2))%>%
  kable_classic()%>%
  column_spec(6, border_right = TRUE)%>%
  row_spec(0, bold = TRUE)%>%
  row_spec(3,hline_after = TRUE)%>%
  row_spec(6, bold = TRUE)%>%
  save_kable('../manuscript/manuscript_files/satlantic_ici_confuseMatrix.png', zoom = 9)

satlantic_alt_confuseMatrix <- rfPermute::confusionMatrix(banter_model_alt_RF)
satlantic_alt_confuseMatrix <- cbind(satlantic_alt_confuseMatrix, priors = satlantic_alt_priors)
satlantic_alt_confuseMatrix <- kable(satlantic_alt_confuseMatrix, align = "c", digits = c(0,0,0,0,2,2,2))%>%
  kable_classic()%>%
  column_spec(5, border_right = TRUE)%>%
  row_spec(0, bold = TRUE)%>%
  row_spec(3,hline_after = TRUE)%>%
  row_spec(5, bold = TRUE)%>%
  save_kable('../manuscript/manuscript_files/satlantic_alt_confuseMatrix.png', zoom = 9)

@@

![BANTER Model S.Atlantic EC Confusion
Matrix](../manuscript/manuscript_files/satlantic_ec_confuseMatrix.png)

![BANTER Model S.Atlantic ICI Confusion
Matrix](../manuscript/manuscript_files/satlantic_ici_confuseMatrix.png)

![BANTER Model S.Atlantic Alternative Model Confusion
Matrix](../manuscript/manuscript_files/satlantic_alt_confuseMatrix.png)

@@

```{r, proximity plot, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
satlantic_ec_proximityPlot <- plotProximity(banter_model_ec_RF)
dev.off()
satlantic_ec_proximityPlot <- plotProximity(banter_model_ec_RF)

png(('../manuscript/manuscript_files/satlantic_ici_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF)
dev.off()
ici_satlantic_proximityPlot <- plotProximity(banter_model_ici_RF)

png(('../manuscript/manuscript_files/satlantic_alt_proximity.png'), width = 20, height = 20, units = 'cm', res = 300)
alt_satlantic_proximityPlot <- plotProximity(banter_model_alt_RF)
dev.off()
alt_satlantic_proximityPlot <- plotProximity(banter_model_alt_RF)
```

@@

```{r, importance heat map, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_ec_RF, plot.type="heatmap")
dev.off()
satlantic_importance <- plotImportance(banter_model_ec_RF, plot.type="heatmap")

png(('../manuscript/manuscript_files/satlantic_ici_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap")
dev.off()
ici_satlantic_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap")

png(('../manuscript/manuscript_files/satlantic_alt_importance.png'), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_alt_RF, plot.type="heatmap")
dev.off()
alt_satlantic_importance <- plotImportance(banter_model_alt_RF, plot.type="heatmap")
```

@@

```{r, plot votes, include=TRUE, results=FALSE}
png(('../manuscript/manuscript_files/satlantic_ec_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_ec_RF)
dev.off()
satlantic_votes <- plotVotes(banter_model_ec_RF)

png(('../manuscript/manuscript_files/satlantic_ici_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_ici_RF)
dev.off()
ici_satlantic_votes <- plotVotes(banter_model_ici_RF)

png(('../manuscript/manuscript_files/satlantic_alt_votes.png'), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_alt_RF)
dev.off()
alt_satlantic_votes <- plotVotes(banter_model_alt_RF)
```

@@

```{r, predicted probabilities, include=TRUE, results=FALSE}
plotPredictedProbs(banter_model_ec_RF, bins=30, plot=TRUE)
plotPredictedProbs(banter_model_ici_RF, bins=30, plot=TRUE)
plotPredictedProbs(banter_model_alt_RF, bins=30, plot=TRUE)
```

Create Figure for Publication
```{r, Publication Figure, include=TRUE}
confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ec_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

satlantic_ec_Figure <-image_append(c(prox, heat, vote))
satlantic_ec_Figure<- image_append(c(confuse, satlantic_ec_Figure), stack=TRUE)
image_write(satlantic_ec_Figure, path = here('manuscript', 'manuscript_files','satlantic_ec_Figure.png'), format ='png')
print(satlantic_ec_Figure, info=FALSE)

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_ici_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

satlantic_ici_Figure <-image_append(c(prox, heat, vote))
satlantic_ici_Figure<- image_append(c(confuse, satlantic_ici_Figure), stack=TRUE)
image_write(satlantic_ici_Figure, path = here('manuscript', 'manuscript_files','satlantic_ici_Figure.png'), format ='png')
print(satlantic_ici_Figure, info=FALSE)

confuse <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_confuseMatrix.png'))%>%
  image_border(color="#ffffff", geometry = "50x130")%>%
  image_annotate("a) Confusion Matrix", size=100, color = "black")
vote <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_votes.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("d) Vote Plot", size=100, color = "black")
prox <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_proximity.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_annotate("b) Proximity Plot", size=100, color = "black")
heat <- magick::image_read(here('manuscript', 'manuscript_files', 'satlantic_alt_importance.png'))%>%
  image_border(color="#ffffff", geometry = "270x130")%>%
  image_scale("3300")%>%
  image_annotate("d) Importance Heat Map", size=100, color = "black")

satlantic_alt_Figure <-image_append(c(prox, heat, vote))
satlantic_alt_Figure<- image_append(c(confuse, satlantic_alt_Figure), stack=TRUE)
image_write(satlantic_alt_Figure, path = here('manuscript', 'manuscript_files','satlantic_alt_Figure.png'), format ='png')
print(satlantic_alt_Figure, info=FALSE)
```
